\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/iteration1.tex
bug fix

As for the qualitative feedback, 11 out of \changes{16} participants preferred IR selection over list mode (\changes{3} preferred list, \changes{2} was undecided). \changes{When asked: \studyquote{When you have multiple candidate targets within sight, which method for selecting between them did you use?} (multiple choices), among 16 participates, 81\% chose {\em adjust head so that only one candidate is signaled}, 56\% chose {\em tap (to enter refinement stage) and then choose between list}, and 25\% chose {\em walk closer to the candidate for a better result}. Although through our observation, many participants walked one or two steps during some tasks, this suggests that participants viewed their moving as a followed-through action of adjusting their heads instead of an intention to walk closer to the targets.

>>>>

As for the qualitative feedback, 11 out of \changes{16} participants preferred IR selection over list mode (\changes{3} preferred list, \changes{2} was undecided). \changes{When asked: \studyquote{When you have multiple candidate targets within sight, which method for selecting between them did you use?} (multiple choices), among 16 participates, 81\% chose {\em adjust head so that only one candidate is signaled}, 56\% chose {\em tap (to enter refinement stage) and then choose between list}, and 25\% chose {\em walk closer to the candidate for a better result}}. Although through our observation, many participants walked one or two steps during some tasks, this suggests that participants viewed their moving as a followed-through action of adjusting their heads instead of an intention to walk closer to the targets.

### 2014-08-14 doc/sui14/sui14.tex
bug fix

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\\textbf{}
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\toappear{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the Owner/Author.\\
\\
Copyright is held by the owner/author(s).\\
\\
{\emph{SUI '14}}, Oct 04-05 2014, Honolulu, HI, USA\\
ACM 978-1-4503-2820-3/14/10.\\
http://dx.doi.org/10.1145/2659766.2659773}

>>>>

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\\textbf{}
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\toappear{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the Owner/Author.\\
%\\
Copyright is held by the owner/author(s).\\
%\\
{\emph{SUI '14}}, Oct 04-05 2014, Honolulu, HI, USA\\
ACM 978-1-4503-2820-3/14/10.\\
http://dx.doi.org/10.1145/2659766.2659773}
